Protein significance analysis of mass spectrometry-based proteomics experiments with R and MSstats (v3.0.10)

### 2015-10-01 MSstats_manual_RMarkdown.Rmd

---
title: "Protein significance analysis of mass spectrometry-based proteomics experiments with R and MSstats (v3.0.9)"
author: "Meena Choi, Tsung-Heng Tsai & Erik Verschueren"
date: "September 24, 2015"
output: pdf_document
bibliography: bibliography.bib
---

>>>>

---
title: "Protein significance analysis of mass spectrometry-based proteomics experiments with R and MSstats (v3.0.10)"
author: "Meena Choi, Tsung-Heng Tsai & Erik Verschueren"
date: "October 01, 2015"
output: pdf_document
bibliography: bibliography.bib
---
